\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Riley Mitchell}}\\
	Melbourne $\cdot$ rileymitch117@gmail.com $\cdot$ 0432553682 $\cdot$ https://github.com/Riz-Mitchell\\
\end{center}

%==== About Me ====%
\header{About Me}
A passionate computer science student with a particular interest in web development. I am eager to work along side and learn from the industries best while I complete my 3rd and final year in my undergraduate degree. I also have a huge drive for competitive swimming which I train for 8 times a week. Recently competing in the 2024 Australian Olympic Trials, I hope to one day qualify for an Australian National Team while I complete my degree and gain more invaluable experience that I can use to further a career as a full stack developer.
\vspace{2mm}

%==== Education ====%
\header{Education}
\textbf{University of Melbourne}\hfill Melbourne, VIC\\
Bachelor of Science, Computing and Software Systems \hfill Feb 2022 - July 2025\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experiecne}
\vspace{1mm}

\textbf{Arena Swimming Melbourne} \hfill Melbourne VIC\\
\textit{Store Manager} \hfill July 2024 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Manage stock.
	\item Assist in administrative tasks.
	\item Oversee sale of world renowned competitive swim suits.
\end{itemize}
\textbf{Kooyong Tennis Club} \hfill Melbourne VIC\\
\textit{Wait Staff} \hfill January 2023 - August 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Interacting with and elating a wide variety of clients and members.
	\item Perform waiter duties in a high stress environment while maintaining strict detail.
	\item Work effectively in a team in a fast paced changing environment.
\end{itemize}
\textbf{Portsea SLSC \textquotesingle{}The Cub\textquotesingle{} Restaurant} \hfill Mornington Peninsula, VIC\\
\textit{Bartender / Wait Staff} \hfill December 2018 - December 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Mixed complex drinks under extremely busy conditions.
	\item Kept track of stock and needs of patrons.
	\item Worked effectively in a team to allow each other to do their respective jobs to the best of their abilities.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages:    & Javascript, Java, Python, C, SQL, HTML, CSS \\
	Technologies:             & Express, Mongoose, MongoDB, SQL, Pandas, Github, Postman, Thunderclient                                      
                \\
	Swimming:                 & Butterfly, Freestyle                                 \\
	General:                  & Teamwork, Coordination, Resilience, Hard Working     \\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Library Management System (ongoing)}} {\sl Node JS, Express, Mongoose, MongoDB, AWS} 
\\
Creating a RESTful API that incorporates JWT authentication for a Library Management System designed to handle inventory, deal with member registrations, manage book loans and host administrative actions.\\
\vspace*{2mm}
{\textbf{Autocomplete Radix Tree}} {\sl C, MAKEFILE}
\\
Developed an Autocomplete Radix Tree in C, implementing a highly efficient data structure with lookup, insertion and deletion operations operations designed to elevate search functionality, providing a way to store strings in a space-time-efficient manner while supporting autocomplete suggestions.\\
\vspace*{2mm}
{\textbf{Parsons Problems Webapp}} {\sl Node JS, Express, Mongoose, MongoDB, AWS} \hfill 
\\
Spearheaded backend development on a Parsons Problems web app, personally implementing a RESTful API that utilizes role based JWT auth to control route access and CRUD operations on user data.\\
\vspace*{2mm}

\header{Awards}
\textbf{Australian Swimming Trials Competitor} \hfill Swimming Australia\\
Competed in the 2024 Australian Olympic Swimming trials \hfill July 2024\\
\vspace*{2mm}
\textbf{Australian Open National SC Finalist} \hfill Swimming Australia\\
Placed 6th in the 2023 Australia Open National Short Course for 200 Butterfly A Final \hfill Sep 2023\\
\vspace*{2mm}

\ 
\end{document}